Figures

### 2019-05-09 figures/07_model-selection.Rmd
explore multivariate predictors

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", 
                "ag_pct", "phosphorus_fertilizer_use", "soybeans")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, !is.na(phosphorusvfertilizervuse), 
                    !is.na(soybeans))

@@

# linear
model_form <- bf(tp ~ agvpct)
fit0 <- get_if_not_exists(brm_fit, "../data/mcmc/fit0.rds", formula = model_form, 
                          data = dt)
print("fixed effect")
print(fit0$formula)

# linear re
model_form <- bf(tp ~ (1 + agvpct | hu4vzoneid))
fit <- get_if_not_exists(brm_fit, "../data/mcmc/fit.rds", formula = model_form, 
                         data = dt)
# plot(fit)
# print(fit$formula)

@@

```{r model_diagnostics_basics, echo=FALSE, fig.height=2}
# get_variables(fit0)
plot(fit0, pars = "agvpct")
```

```{r model_diagnostics_advanced, fig.height=4, echo=FALSE}
# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_agvpct) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_agvpct, c(0.05, 0.5, 0.95)))))

# pull hu4 distribution (lower, mean, upper)
hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "agvpct") %>%
  group_by(hu4vzoneid) %>%
  do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
  mutate(signif = case_when(`5%` > 0 ~ TRUE))

@@

# loo significance testing
loo0 <- loo(fit)
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo0, loo1)
loo_compare(loo1, loo2)
```

>>>>

dt        <- readRDS("../data/dt.rds") %>% 
  dplyr::select("lagoslakeid", "hu4_zoneid", "tp", "hu12_ppt_mean", 
                "maxdepth", "iwsla_ratio", "ag", "row_crop_pct", "corn", 
                "soybeans", "pasture", 
                "phosphorus_fertilizer_use", "nitrogen_fertilizer_use")
names(dt) <- gsub("_", "v", names(dt))
dt        <- dplyr::filter(dt, 
                           !is.na(phosphorusvfertilizervuse), 
                           !is.na(soybeans), 
                           !is.na(maxdepth), 
                           !is.na(tp))
dt <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))

@@

# linear
model_form <- bf(tp ~ ag)
# unlink("../data/mcmc/fit0.rds")
fit0 <- get_if_not_exists(brm_fit, "../data/mcmc/fit0.rds", formula = model_form, 
                            data = dt)
print("fixed effect")
print(fit0$formula)

# linear re
model_form <- bf(tp ~ (1 + ag | hu4vzoneid))
# unlink("../data/mcmc/fit.rds")
fit <- get_if_not_exists(brm_fit, "../data/mcmc/fit.rds", formula = model_form, 
                         data = dt)
# plot(fit)
# print(fit$formula)

# linear re with focal predictor
model_form <- bf(tp ~ maxdepth + (1 + ag | hu4vzoneid))
# unlink("../data/mcmc/fit1.rds")
fit1 <- get_if_not_exists(brm_fit, "../data/mcmc/fit1.rds", formula = model_form, 
                         data = dt)
# plot(fit1)
# print(fit$formula)

# linear re with multivariate focal predictor
model_form <- bf(tp ~ maxdepth + iwslavratio + (1 + ag | hu4vzoneid))
# unlink("../data/mcmc/fit2.rds")
fit2 <- get_if_not_exists(brm_fit, "../data/mcmc/fit2.rds", formula = model_form, 
                         data = dt)
# plot(fit1)
# print(fit$formula)

loo_compare(loo(fit1), loo(fit2))

range(dt$iwslavratio)

range((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
hist((dt$iwslavratio - mean(dt$iwslavratio)) / sd(dt$iwslavratio))
test <- mutate_at(dt, scale, .vars = vars(-lagoslakeid, -hu4vzoneid))

@@

```{r model_diagnostics_basics, echo=FALSE, fig.height=2}
# get_variables(fit0)
plot(fit0, pars = "ag")
```

```{r model_diagnostics_advanced, fig.height=4, echo=FALSE}
# pull global distribution (lower, mean, upper)
# get_variables(fit0)
global_dist <- spread_draws(fit0, b_ag) %>%
    mutate(hu4vzoneid = "global") %>%
    group_by(hu4vzoneid) %>%
    do(tibble::as_tibble(t(quantile(.$b_ag, c(0.05, 0.5, 0.95)))))

# pull hu4 distribution (lower, mean, upper)
hu4_dist <- spread_draws(fit, r_hu4vzoneid[hu4vzoneid,term]) %>%
  dplyr::filter(term == "ag") %>%
  group_by(hu4vzoneid) %>%
  do(tibble::as_tibble(t(quantile(.$r_hu4vzoneid, c(0.05, 0.5, 0.95))))) %>%
  mutate(signif = case_when(`5%` > 0 ~ TRUE))

@@

# loo significance testing
loo  <- loo(fit)
loo0 <- loo(fit0)
loo1 <- loo(fit1)
loo2 <- loo(fit2)
loo_compare(loo0, loo1)
loo_compare(loo1, loo2)
```
